Jackknife

### 2021-03-05 analysis/rev_prototyping/jacknife_results.Rmd

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1))

jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))

jk_di <- jk_di_full %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup() %>%
  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingeltons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

all_di_actual <- all_di %>%
  filter(!singletons) %>%
  mutate(site_source = as.character(site)) %>%
  select(dat, site_source, s0, n0, skew_percentile_excl, skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons,nsingeltons_median,  nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

jk_di_mean_results <- jk_di_mean_results %>%
  mutate(skew_actual_sig = skew_percentile_excl_actual > 95,
         skew_sig = skew_percentile_excl > 95) %>%
  mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig)) %>%
  filter(nparts > 20)

@@

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_shannon_high_jk = mean(shannon_percentile > 95),
            prop_shannon_high_raw = mean(shannon_percentile_actual > 95),
            prop_shannon_low_jk = mean(shannon_percentile< 5),
            prop_shannon_low_raw = mean(shannon_percentile_actual < 5),
            nsites_included = dplyr::n())

@@

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile > 95),
            prop_mean_po_comparison_high_raw = mean(mean_po_comparison_percentile_actual > 95),
            nsites_included = dplyr::n())

@@

<!-- ```{r, fig.dim = c(6,6)} -->

>>>>

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
  filter(nparts > 20)

jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
  filter(nparts > 20)

jk_di <- jk_di_full %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup() %>%
  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile,shannon_percentile_excl,  nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims,mean_po_comparison_percentile_excl, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

all_di_actual <- all_di %>%
  filter(!singletons) %>%
  mutate(site_source = as.character(site)) %>%
  select(dat, site_source, s0, n0, skew_percentile_excl, skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl, nsingletons,  nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95,mean_po_comparison_percentile_excl, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

# jk_di_mean_results <- jk_di_mean_results %>%
#   mutate(skew_actual_sig = skew_percentile_excl_actual > 95,
#          skew_sig = skew_percentile_excl > 95) %>%
#   mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig)) %>%
#   filter(nparts > 20)

@@

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_shannon_high_jk = mean(shannon_percentile_excl > 95),
            prop_shannon_high_raw = mean(shannon_percentile_excl > 95),
            prop_shannon_low_jk = mean(shannon_percentile< 5),
            prop_shannon_low_raw = mean(shannon_percentile_actual < 5),
            nsites_included = dplyr::n())

@@

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile_excl > 95),
            prop_mean_po_comparison_high_raw = mean(mean_po_comparison_percentile_excl_actual > 95),
            nsites_included = dplyr::n())

@@

<!-- ```{r, fig.dim = c(8,8)} -->

<!-- fia_max_n = 150 -->
<!-- fia_max_s = 21 -->

<!-- ggplot(jk_di_mean_results, aes(s0, n0, color = dat)) + -->
<!--   geom_point(aes(s0_actual, n0_actual), color = "grey", alpha  = .2)+ -->
<!--     geom_point(aes(s0, n0, color = dat), alpha = .5) + -->
<!--   theme_bw() + -->
<!--   scale_x_log10() + -->
<!--   scale_y_log10() + -->
<!--   facet_wrap(vars(dat)) + -->
<!--   geom_vline(xintercept = fia_max_s) + -->
<!--   geom_hline(yintercept = fia_max_n) + -->
<!--   theme(legend.position = "top") -->

<!-- jk_di_mean_results <- jk_di_mean_results %>% -->
<!--   group_by_all() %>% -->
<!--   mutate(fiasized = (s0 <= fia_max_s) && (n0 <= fia_max_n), -->
<!--          fiasized_acutal =(s0_actual <= fia_max_s) && (n0_actual <= fia_max_n) ) %>% -->
<!--   ungroup() -->

<!-- jk_di_mean_results %>% -->
<!--   group_by(dat) %>% -->
<!--   summarize(jk_small = mean(fiasized), actual_small = mean(fiasized_acutal), nsites = dplyr::n()) -->

<!-- jk_di_mean_results %>% -->
<!--   group_by(dat, fiasized) %>% -->
<!--   summarize( nsingletons_high  = mean(nsingletons_percentile_excl > 95), nsites = dplyr::n()) -->

<!-- ``` -->
<!-- ```{r, fig.dim = c(6,6)} -->
